Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Edit final sample and result 1

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny E. Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        \newauthor
        Yen-Ting Lin,$^{5}$
        Masayuki Tanaka,$^{5}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        \newauthor
        Yutaka Komiyama,$^{5,8}$
        HSC collaboration 
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
      \caption{
          \textbf{Left}: Median \mden{} profiles in three total stellar mass bins. 
              Thin grey lines show a random subset of individual profiles.  The scatter between the thin grey lines reflects the true scatter in the profiles of massive galaxies (not measurement error). The shaded region highlights the region that could be affected by the PSF. \rachel{`most strongly' affected?}
              Two vertical lines indicate 10 kpc (thin, dotted line) and
              100 kpc (thick, dashed line). ~~~ 
          \textbf{Right}: comparison between our \mden{} profiles, previous observations, 
              and simulations. 
              The solid cyan line shows the median profile of massive elliptical 
              galaxies at $z{\sim} 0$ from \citet[][]{Huang2013a}. 
              The red long-dashed line shows the median profile of massive galaxies at 
              $0.25 \leq z < 0.50$ observed by \textit{HST} from \citet[][]{Patel2013}. 
              The purple short-dashed line shows the median radial stellar distributions 
              in massive halos from simulation using the particle tagging method
              (\citealt{Cooper2013}).}
      \label{fig:avg_prof}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Fig.~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
    profiles along with their uncertainties are derived using bootstrap resampling. \rachel{Why is this a footnote?  It's a major feature of the plot, not a minor detail.  Same comment applies to footnote below this.}} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
    bins\footnote{Note that our sample is not complete in our lowest \mtot{} bin.}. 
    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
    the \mden{} profiles of these massive galaxies out to 100 kpc 
    \textbf{individually}.  At large scales, some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
    related to inaccurate sky subtraction. In this paper, we do not use profiles beyond 100 kpc, even though the median 
    \mden{} profiles for the two most massive bins behave reasonably out to 
    ${\sim} 200$ kpc.

@@

    Finally, we also compare with the predicted median \mden{} profile of central 
    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from a cosmological 
    simulation where the \mden{} profiles of galaxies are calculated using the 
    particle-tagging technique (e.g., \citealt{Cooper2010}). 
    The simulated \mden{} profile is affected by the resolution limit of the simulation in the inner region, but  is in good agreement with our median \mden{} profile for 
    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
    However, outside 40 kpc, the particle tagging method seems to predict a too 
    prominent stellar halo and has much shallower outer slope compared to our data. In future work, we will compare  our HSC profiles with  predictions from more advanced 
    hydrodynamic simulations such as Horizon-AGN () and MassiveBlackII (). These data will help fine-tune simulations and to understand the physical mechanisms that drive the assembly of massive galaxies and the 
    build up of stellar halos.

@@

  % Personal 
  The authors thank Frank van~den~Bosch for insightful discussions.
  SH thanks F.S.Liu for sharing the data from his work.

>>>>

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny E. Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        \newauthor
        Yen-Ting Lin,$^{5}$
        Masayuki Tanaka,$^{5}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        \newauthor
        Yutaka Komiyama$^{5,8}$
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
      \caption{
          \textbf{Left}: Median \mden{} profiles in three total stellar mass bins. 
              Thin grey lines show a random subset of individual profiles.  
              The scatter between the thin grey lines reflects the true scatter in 
              the profiles of massive galaxies (not measurement error). 
              The shaded region highlights the region that is most strongly affected 
              by the seeing. 
              Two vertical lines indicate 10 kpc (thin, dotted line) and
              100 kpc (thick, dashed line). ~~~ 
          \textbf{Right}: comparison between our \mden{} profiles, previous observations, 
              and simulations. 
              The solid cyan line shows the median profile of massive elliptical 
              galaxies at $z{\sim} 0$ from \citet[][]{Huang2013a}. 
              The red long-dashed line shows the median profile of massive galaxies at 
              $0.25 \leq z < 0.50$ observed by \textit{HST} from \citet[][]{Patel2013}. 
              The purple short-dashed line shows the median radial stellar distributions 
              in massive halos from simulation using the particle tagging method
              (\citealt{Cooper2013}).}
      \label{fig:avg_prof}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Fig.~\ref{fig:avg_prof} shows the median \mden{} profiles of massive central 
    galaxies at $0.3 < z < 0.5$ in three \mtot{} bins.
    These median profiles along with their uncertainties are derived using bootstrap
    resampling method. 
    And it is worth pointing out again that our sample is not complete in the lowest 
    \mtot{} bin, although there is no reason to believe the median \mden{} profile
    will be significantly affected. 
    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
    the \mden{} profiles of these massive galaxies out to 100 kpc \textbf{individually}.  
    At large scales, some of our \mden{} profiles show signs of unphysical truncation and
    fluctuation related to inaccurate sky subtraction. 
    In this paper, we do not use profiles beyond 100 kpc, even though the median 
    \mden{} profiles for the two most massive bins behave reasonably out to 
    ${\sim} 200$ kpc.

@@

    Finally, we also compare with the predicted median \mden{} profile of central 
    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from a cosmological 
    simulation where the \mden{} profiles of galaxies are calculated using the 
    particle-tagging technique (e.g., \citealt{Cooper2010}). 
    The simulated \mden{} profile is affected by the resolution limit of the simulation 
    in the inner region, but is in good agreement with our median \mden{} profile for 
    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
    However, outside 40 kpc, the particle tagging method seems to predict a too 
    prominent stellar halo and has much shallower outer slope compared to our data. 
    In future work, we will compare our HSC profiles with predictions from more 
    advanced hydrodynamic simulations such as \textit{Horizon-AGN} (\citealt{Dubois2014}) 
    and MassiveBlackII (\citealt{Khandai2015}). 
    These data will help fine-tune simulations and to understand the physical mechanisms 
    that drive the assembly of massive galaxies and the build up of stellar halos.

@@

  % Personal 
  The authors thank Frank van~den~Bosch for insightful discussions and thank 
  Shun Saito for helping us estimate the fraction of satellite galaxies in our sample.
  SH thanks Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
  his work.
